Association between wildfire smoke and asthma claims by place of service

### 2018-09-04 r_scripts/analysis/asthma_place_of_service_analysis.Rmd
updated main result plot for job talk

>>>>

Plot for job talk presentation.

```{r total_strata_plot}
# filter out amublance since the values are skewed
plot_df <- sameday_result %>% filter(service_place != 'Ambulance-Land')

plot <- ggplot(plot_df, aes(x = service_place, y = estimate)) +
  geom_point(color = "#3c1053") + 
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                color = "#3c1053",width = 0.2) +
  geom_hline(yintercept = 1, linetype=2) +
  ylab(expression(paste("Odds Ratio for 10µg/m"^3, 
                        " Increase in WFS PM"[2.5]))) +
  xlab("Place of Service") +
   # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element (tilt)
    axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.7),
    #axis.title.x = element_blank(),
    #axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90))

# print plot
plot
#ggsave("./Figs/asthma_pos_total.tiff", plot, 
#       units="in", width=8, height=6, dpi=300)
```
